This thesis is based on the following publications and proceedings.

\paragraph{Awards and notable mentions}

\begin{itemize}
    \item \textbf{Where is my URI?} (Honorable mentioned) \cite{valdestilhas2018my}
    \item \textbf{Triple scoring using a hybrid fact validation approach} (WSDM cup - 3th place) \cite{marx2017triple}
\end{itemize}

\paragraph{conferences, peer-reviewed}

\begin{itemize}
    \item \textbf{DBpediaSameAs: An approach to tackle heterogeneity in DBpedia identifiers.} \cite{valdestilhas2015dbpediasameas}
    \item \textbf{A High-Performance Approach to String Similarity using Most Frequent K Characters} \cite{valdestilhas2017high}
    \item \textbf{CEDAL: time-efficient detection of erroneous links in large-scale link repositories} \cite{valdestilhas2017cedal}
    \item \textbf{Where is my URI?} \cite{valdestilhas2018my}
    \item \textbf{More complete resultset retrieval from large RDF datasets} \cite{ValdestilhasKcap}
    \paragraph{As co-author}
    \begin{itemize}
        \item \textbf{SPARQL as a Foreign Language} \cite{soru2017sparql}
        \item \textbf{WASOTA} What Are The State Of The Art for? \cite{neto2016wasota}
        \item \textbf{Generating a large dataset for neural question answering over the dbpedia knowledge base}        \cite{hartmann2018generating}
        \item \textbf{Neural Machine Translation for Query Construction and Composition} \cite{soru2018neural}
        \item \textbf{Semantic search user interface patterns: an introduction} \cite{marx2017semantic}
        \item \textbf{Where is Linked Data in Question Answering over Linked Data?} \cite{soru2020linked}
    \end{itemize}
\end{itemize}

\paragraph{Project proposal based on this thesis}
\begin{itemize}
    \item ReLOD project. Participating on the \textit{Next Generation Internet initiative}\footnote{Next Generation Internet initiative. \url{https://nlnet.nl/propose/}}
\end{itemize}

\paragraph{Under-review}

\begin{itemize}
    \item Identifying, Querying, and Relating Large Heterogeneous RDF Sources. Submitted to Semantic Web Journal on March 31, 2020\cite{valdestilhasSWJ2020}.
    \item \textsc{ShaclEditor} - An integrated environment for Visualizing, Validate, and Versioning RDF graph. Submitted to VOILA workshop at ISWC, 2020\cite{valdestilhasISWC2020}.
    %\item \textsc{ReLOD} - The incremental LOD Dataset relation index. Submitted to ISWC 2020.
    %\item Detecting Erroneous Link candidates in Educational Link Repositories - ESWC - LASCAR workshop 2020.
\end{itemize}